% THIS DOCUMENT IS FOLLOWS THE VOLERE TEMPLATE BY Suzanne Robertson and James Robertson
% ONLY THE SECTION HEADINGS ARE PROVIDED
%
% Initial draft from https://github.com/Dieblich/volere
%
% Risks are removed because they are covered by the Hazard Analysis
\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
      colorlinks=true,      % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\newcommand{\lips}{\textit{Insert your content here.}}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Software Requirements Specification for \progname: subtitle describing software} 
\author{\authname}
\date{\today}
	
\maketitle

~\newpage

\pagenumbering{roman}

\tableofcontents

~\newpage

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\textbf{Date}} & {\textbf{Version}} & {\textbf{Notes}}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\\

~\newpage
\section{Purpose of the Project}
\subsection{User Business}
\lips
\subsection{Goals of the Project}
\lips
\section{Stakeholders}
\subsection{Client}
\lips
\subsection{Customer}
\lips
\subsection{Other Stakeholders}
\lips
\subsection{Hands-On Users of the Project}
\lips
\subsection{Personas}
\lips
\subsection{Priorities Assigned to Users}
\lips
\subsection{User Participation}
\lips
\subsection{Maintenance Users and Service Technicians}
\lips

\section{Mandated Constraints}
\subsection{Solution Constraints}
\lips
\subsection{Implementation Environment of the Current System}
\lips
\subsection{Partner or Collaborative Applications}
\lips
\subsection{Off-the-Shelf Software}


There are several existing solutions that could serve as part of the music generation and recommendation system. These include:

\begin{itemize}
    \item \textbf{Spotify API}: Provides access to a vast library of music, including song previews and metadata, which can be leveraged for generating recommendations.
    \item \textbf{Librosa Library}: An open-source Python package for analyzing and processing music files, suitable for extracting features from songs and facilitating generative components.
    \item \textbf{TensorFlow and PyTorch Pre-trained Models}: Both frameworks offer pre-trained models that could be adapted for music generation tasks. These solutions provide a basis for deep learning models without having to build and train from scratch.
    \item \textbf{OpenAI Jukebox}: A generative model that is capable of producing music, which could potentially be adapted and integrated into our system.
\end{itemize}

These off-the-shelf software solutions provide a foundation upon which we can build our custom features, significantly reducing the development time and leveraging existing technologies to enhance the functionality of our platform.

\subsection{Anticipated Workplace Environment}
\lips
\subsection{Schedule Constraints}
\lips
\subsection{Budget Constraints}
\lips
\subsection{Enterprise Constraints}
\lips

\section{Naming Conventions and Terminology}
\subsection{Glossary of All Terms, Including Acronyms, Used by Stakeholders
involved in the Project}
\lips

\section{Relevant Facts And Assumptions}
\subsection{Relevant Facts}
\lips
\subsection{Business Rules}
\lips
\subsection{Assumptions}
\lips

\section{The Scope of the Work}
\subsection{The Current Situation}
\lips
\subsection{The Context of the Work}
\lips
\subsection{Work Partitioning}
\lips
\subsection{Specifying a Business Use Case (BUC)}
\lips

\section{Business Data Model and Data Dictionary}
\subsection{Business Data Model}
\lips
\subsection{Data Dictionary}
\lips

\section{The Scope of the Product}
\subsection{Product Boundary}
\lips
\subsection{Product Use Case Table}
\lips
\subsection{Individual Product Use Cases (PUC's)}
\lips

\section{Functional Requirements}
\subsection{Functional Requirements}
\lips

\section{Look and Feel Requirements}
\subsection{Appearance Requirements}
\lips
\subsection{Style Requirements}
\lips

\section{Usability and Humanity Requirements}
\subsection{Ease of Use Requirements}
\lips
\subsection{Personalization and Internationalization Requirements}
\lips
\subsection{Learning Requirements}
\lips
\subsection{Understandability and Politeness Requirements}
\lips
\subsection{Accessibility Requirements}
\lips

\section{Performance Requirements}
\subsection{Speed and Latency Requirements}
\lips
\subsection{Safety-Critical Requirements}
\lips
\subsection{Precision or Accuracy Requirements}
\lips
\subsection{Robustness or Fault-Tolerance Requirements}
\lips
\subsection{Capacity Requirements}
\lips
\subsection{Scalability or Extensibility Requirements}
\lips
\subsection{Longevity Requirements}
\lips

\section{Operational and Environmental Requirements}
\subsection{Expected Physical Environment}
\lips
\subsection{Wider Environment Requirements}
\lips
\subsection{Requirements for Interfacing with Adjacent Systems}
\lips
\subsection{Productization Requirements}
\lips
\subsection{Release Requirements}
\lips

\section{Maintainability and Support Requirements}
\subsection{Maintenance Requirements}
\lips
\subsection{Supportability Requirements}
\lips
\subsection{Adaptability Requirements}
\lips

\section{Security Requirements}
\subsection{Access Requirements}
\lips
\subsection{Integrity Requirements}
\lips
\subsection{Privacy Requirements}
\lips
\subsection{Audit Requirements}
\lips
\subsection{Immunity Requirements}
\lips

\section{Cultural Requirements}
\subsection{Cultural Requirements}
\lips

\section{Compliance Requirements}
\subsection{Legal Requirements}
\lips
\subsection{Standards Compliance Requirements}
\lips

\section{Open Issues}
\lips

\section{Off-the-Shelf Solutions}
\subsection{Ready-Made Products}
\lips
\subsection{Reusable Components}
\lips
\subsection{Products That Can Be Copied}
\lips

\section{New Problems}

\subsection{Effects on the Current Environment}

The platform's high computational requirements, especially during the training and usage of generative models, may put a strain on existing computational resources. This could lead to slower performance for other applications that share these resources. Additionally, increased data transmission due to the integration with APIs such as Spotify and Deezer could lead to higher network bandwidth utilization, potentially affecting the performance of other network-dependent systems. Mitigating these effects may require infrastructure scaling, such as increasing server capacity or optimizing data processing, to ensure that the existing systems are not disrupted.

\subsection{Effects on the Installed Systems}

The new platform will interact with various installed systems, leading to the introduction of new dependencies. For example, using third-party APIs like Spotify or integrating machine learning frameworks such as TensorFlow may require changes to the current software stack. These dependencies could introduce compatibility issues, particularly if third-party providers update their APIs or if new versions of required libraries are released. Such updates might necessitate timely system changes to maintain functionality and avoid disruptions. Ensuring that installed systems remain compatible requires diligent version management, comprehensive testing, and a structured process for managing library and API updates.

\subsection{Potential User Problems}

The platform is designed to offer advanced features, which may present usability challenges for some users. For example, users with limited technical skills may struggle to understand the process of modifying musical features like key, rhythm, or tempo, which are essential for customizing music generation. Furthermore, the quality of generated outputs is inherently subjective, and users may feel frustrated if the system-generated music does not meet their expectations. Another potential problem is system latency, especially when resource-intensive operations like model inference are being performed. Long waiting times could negatively impact user experience, making the platform feel less responsive, which may deter regular use.

\subsection{Limitations in the Anticipated Implementation Environment That May Inhibit the New Product}

The platform is expected to be implemented on a local server, which presents certain limitations. The local server environment will need sufficient processing power to handle computationally intensive tasks, such as model training and music generation. If the server infrastructure is under-resourced, performance issues such as latency and reduced processing speed could arise. Additionally, reliance on a local server means that the platform's effectiveness is tied directly to server availability and maintenance. Any server downtime could render the platform inaccessible to users. If we decide to extend the platform's implementation onto personal devices, new limitations arise. Personal devices, especially those with limited hardware capabilities, may struggle with the computational requirements of generative music models, leading to significant performance bottlenecks. This could make the platform inaccessible or difficult to use for some users. Moreover, the reliance on internet connectivity for accessing external APIs is another major limitation. Users in areas with unreliable internet or low bandwidth may face difficulties, particularly with real-time features like music recommendations or generating new songs based on streaming data. These limitations could restrict the user base to only those with high-performance devices and stable internet connections.

\subsection{Follow-Up Problems}

Once the platform is deployed, several follow-up issues will need to be addressed to maintain and improve the product. One of the primary challenges will be keeping up with third-party API changes, such as modifications to Spotify or Deezer APIs, which could lead to broken features if not handled promptly. The generative models used by the platform will also require regular updates and retraining to stay relevant to emerging musical styles and user preferences. Another follow-up problem is related to usability: feedback from users might reveal unforeseen pain points or desired improvements. Addressing these concerns will require an iterative development approach, incorporating user feedback into future versions of the platform to enhance usability and performance.


\lips
\subsection{Follow-Up Problems}
\lips

\section{Tasks}
\subsection{Project Planning}
\lips
\subsection{Planning of the Development Phases}
\lips

\section{Migration to the New Product}
\subsection{Requirements for Migration to the New Product}
\lips
\subsection{Data That Has to be Modified or Translated for the New System}
\lips

\section{Costs}
\lips
\section{User Documentation and Training}

\subsection{User Documentation Requirements}

To ensure that users can effectively interact with the music generation and recommendation platform, the following user documentation will be provided:

\begin{itemize}
    \item \textbf{User Manual}: A comprehensive guide explaining the functionalities of the platform, including step-by-step instructions on generating music, adjusting parameters, and using the recommendation features.
    \item \textbf{Quick Start Guide}: A concise guide aimed at helping new users get started with the basics of generating and recommending music.
    \item \textbf{FAQs and Troubleshooting}: A list of frequently asked questions and troubleshooting tips to help users solve common issues independently.
    \item \textbf{Video Tutorials}: Step-by-step video guides that visually demonstrate key features and workflows.
\end{itemize}

These documents will be designed for users of varying technical backgrounds to ensure they can fully utilize the platform's capabilities.

\subsection{Training Requirements}

To provide users with sufficient knowledge to operate the platform effectively, the following training resources will be developed:

\begin{itemize}
    \item \textbf{Interactive Training Sessions}: These sessions, either virtual or in-person, will help users—especially music producers and educators—get hands-on experience with the platform’s features.
    \item \textbf{Webinars}: Webinars will be organized to introduce new features, answer user questions, and provide additional insights into advanced usage. They will be recorded for repeat usage.
    \item \textbf{Training Workshops}: Workshops will be conducted for stakeholders to offer deeper knowledge, with a focus on leveraging the platform for specific needs, such as music production or sound design.
\end{itemize}

These training requirements aim to encourage users to explore the full potential of the platform, regardless of their prior experience in music production or technology.


\section{Waiting Room}
\lips

\section{Ideas for Solution}

\begin{itemize}
    \item \textbf{Hybrid Recommendation System}: 
    A hybrid recommendation system combines content-based filtering and collaborative filtering techniques to provide a more personalized experience for users. Content-based filtering analyzes song features, such as genre, key, and rhythm, to suggest similar tracks. Collaborative filtering uses user preferences and historical listening patterns to suggest music. By combining these approaches, the system can offer users personalized suggestions while also helping them discover new genres and music styles.

    \item \textbf{Generative Music Model}: 
    To enable the creation of new music, a generative model will be used. This model could be based on techniques such as a Generative Adversarial Network (GAN) or Recurrent Neural Network (RNN). A GAN would allow for the generation of realistic music by having the generator and discriminator work together to produce convincing compositions. An RNN, on the other hand, would be well-suited for learning the sequential nature of music, generating new melodies based on learned patterns. This solution provides users with an innovative way to create new music based on their inputs and preferences.

    \item \textbf{Feature Manipulation Interface}: 
    This interface will allow users to interact directly with song features, such as tempo, key, and rhythm, enabling them to create customized versions of existing tracks or generate entirely new compositions. By adjusting different musical parameters, users can personalize their musical experience and experiment with creative variations, providing a high level of control over the output.

    \item \textbf{Integration with Existing Platforms}: 
    Integrating the system with existing music platforms, such as Spotify, will allow users to easily access and analyze a large library of songs. Users will be able to input their favorite tracks from these platforms and generate variations or receive recommendations. This integration ensures a smooth user experience, allowing seamless interaction between existing music libraries and the platform's generative capabilities.

\end{itemize}


\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Lifelong Learning.  Please answer the following questions:

\begin{enumerate}
  \item What knowledge and skills will the team collectively need to acquire to
  successfully complete this capstone project?  Examples of possible knowledge
  to acquire include domain specific knowledge from the domain of your
  application, or software engineering knowledge, mechatronics knowledge or
  computer science knowledge.  Skills may be related to technology, or writing,
  or presentation, or team management, etc.  You should look to identify at
  least one item for each team member.
  \item For each of the knowledge areas and skills identified in the previous
  question, what are at least two approaches to acquiring the knowledge or
  mastering the skill?  Of the identified approaches, which will each team
  member pursue, and why did they make this choice?
\end{enumerate}

\end{document}